Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-06-06 reply_to_reviews.tex

\blue
I think the term ‘propriety’ (as in having the property of being proper) should either be explicitly defined or re-worded in terms of ‘being proper’.

\black
We reworded occurences of the term `propriety'.

\red
No reference is provided for the approximate variance-stabilising properties of the square root transformation.

\black
We added a reference to the following book:
Dunn, P.K., Smyth, G.K.(2018). Generalized Linear Models With Examples in R. Germany: Springer New York, page 118.

\url{https://www.google.fr/books/edition/Generalized_Linear_Models_With_Examples/tBh5DwAAQBAJ?hl=en&gbpv=1&dq=variance-stabilizing+transformation+square+root&pg=PA119&printsec=frontcover}, page 118

@@

\red
Additionally, any additional necessary/recommended elements of a scoring procedure should be noted more prominently (e.g., dealing with forecast missingness, outlying forecasts, outlying data, selecting a Box-Cox transformation, selecting a shift ($a$ value), etc.).

\black
Hm potentially an interesting point. At the moment the paper kind of assumes you know what you're doing and suggests to do it differently. One could I guess add a paragraph that walks through all the steps? Add it where? Maybe this should be done in another piece that talks about best practices?

\red

\subsection{Major comments}
\blue
``Natural logarithm'', log1p, and log($a + x$) are conflated in several places, despite the discussion in Section 2.4 noting that this is an important distinction. The terminology should not be overloaded. (E.g., L20 ``Applying the log transformation''.)

\black
L20 refers to the abstract. We changed ``Applying the log transformation'' to ``Applying a transformation of log($x + 1$)''.

We slightly disagree with the notion that the terminology should not be overloaded. Not introducing another term for transformations of $\log_{e}(x + \varepsilon)$ makes the manuscript more readable and accessible to readers. In addition, our analyses suggest that adding a small context doesn't make much of a difference in most practical applications. We nevertheless completely agree that this should be made clear to the reader and have added the following text:

\textit{For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation in the context of epidemic phenomena. We refer to this transformation as 'log-transformation' and to scores that have been log-transformed as scores 'on the log scale' (as opposed to scores 'on the natural scale', which have not been transformed). In the theoretical discussion in Section \ref{sec:methods}, 'log-transformation' and 'log scale' generally refer to a transformation of $\log_{e}(x)$. For practical applications (Section \ref{sec:HUB}) we also use these terms to describe a transformation of $\log_{e}(x + \varepsilon)$ in order to keep the notation simple.}

@@

Regarding the question which transformations are permissible:

Johannes: scaling by recent observations is okay and in a way that's what we are doing with the log (very similar to scaling with last value).Scaling by population size is okay as mentioned in discussion. Scaling with forecast or observation is not okay (I could probably find examples for that).
Paper Sebastian Lerch?

Do we need to update anything in the manuscript?

\blue
L166: “a negative binomial distribution with size parameter $\theta$” — Is this realistic? If so, what’s the interpretation epidemiologically?

\black
This is an illustrative example and is not meant to be completely realistic. Rather, the point is to illustrate that for observations which have a standard deviation that grows linearly with the mean, the log transformation can serve as a variance-stabilising transformation. However, negative binomial distributions / Poisson gamma mixtures have been used in the past (see e.g. \url{https://doi.org/10.1111/rssa.12974}) to model epidemiological processes. We agree with the reviewer that a size parameter of 0.1 is not realistic, but still think that the example is valuable as an illustration.

\blue
Figure 3: is a geometric distribution realistic for epidemiological surveillance data?

\black
Again, we agree that this is not a typical example we would expect to see in an epidemiological setting. It could happen in principle, but only in rather constructed cases. We still believe the example is valuable to illustrate the general point that the rankings between two forecasts can change even for a single observation.

@@

\red
Figure 4: The data (not) selected seems to obscure the key period of predicting the start of a case wave, as we expect the CRPS of log data to emphasize missed case increase predictions there more heavily than the natural scale. Deaths are not a substitute because they have access to a leading indicator and the same sort of misses may not be observed. The evaluations here may also miss some overshooting of the case peak. Which rules from Table SI.2 are coming into play and why? Is there a more complete alternative example?

\black
The data that was removed here was largely due to data revisions, not due to forecasts removed by the filtering. 
We added the percentages of observed values in the main text and added the following two Figures in the SI to make that clearer.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.49\textwidth]{output/figures/number-anomalies.png}
     \includegraphics[width=0.49\textwidth]{output/figures/erroneous-forecasts.png}
     \caption{}
    \label{fig:number-anomalies}
\end{figure}

\blue
Table 1: The beta for cases and beta for deaths are both around 0.86 individually. But fit together they beta is 0.963; this appears due to trying to fit two different (difficulties of) tasks together that follow different trends, evident from the differing alpha values. A joint fit does not seem appropriate without allowing for a separate alpha per task type. The same thing can be said for the different horizons within cases\&deaths. The fits here seem to better support an argument for something between sd and log.

\black
We agree with the point, thank you for raising it. We removed the joint fit from the table.

@@

\blue
L60: “immunity” $\xrightarrow{}$ “population immunity”?

\black
We changed this to "population immunity" as suggested.

\red
L69: This might benefit from a short justification (e.g.,
$\left| \frac{x_t e^{(r_t + \epsilon) \Delta t} - x_t e^{r_t \Delta t}}{x_t e^{(r_t - \epsilon) \Delta t} - x_t e^{r_t \Delta t}} \right| = e^{\epsilon\Delta t}$)

\black
This is a great suggestion, thank you. We updated the corresponding paragraph, which now reads:

\textit{If case numbers are evolving based on an exponential process and the  modelling task revolves around estimating and forecasting the reproduction number or the corresponding growth rate, then evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number or growth rate) less than overprediction by the same amount. Consider a forecast that misses the correct growth rate by either $+\epsilon$ or $-\epsilon$:}

\begin{equation}
\left| \frac{x_t e^{(r_t + \epsilon) \Delta t} - x_t e^{r_t \Delta t}}{x_t e^{(r_t - \epsilon) \Delta t} - x_t e^{r_t \Delta t}} \right| = e^{\epsilon\Delta t}
\end{equation}

\textit{For exponential processes errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate.}

\black
L70: Clarify: is this suggesting to make the forecasting targets themselves the result of applying some standardized growth rate estimator to current+future observations around the desired time period?

\black 
Here we aren't suggesting a specific transformation yet, but rather just say that it would be desirable to score a forecast of the growth rate (regardless of how that can be achieved). Specific suggestions for how to achieve this (either by taking a log transformation or by using another transformation to obtain growth rates directly as mentioned in the Discussion) are discussed in more detail in the remainder of the text. We added the word 'conceptually' to the sentence to make this a bit clearer.

@@

\red

L138: “$\Bar{r}$ is” — Consider $\Bar{r}_t$ etc.

L146: “$\Bar{\hat{r}}$” — Should be $\hat{\Bar{r}}$, or consider $\hat{\Bar{r}}_t$.

\black
We applied the suggested changes.

\red
L158 “delta method” — Delta method would seem to also require the distribution to be somewhat tightly distributed, concentrated within a nearly-linear region of the transformation function. But putting significant mass on a wider range of values would also mean having non-negligible mass on negative values if “approximately normal”; it would not make sense to apply the logarithm or sqrt transformations in these cases. So perhaps the “tightly distributed” assumption can be taken. But this seems a bit nonobvious and a justification/application of the delta method would be helpful here.

@@

\black
While not proved here this is a statement that holds generally. Johaaannes? Also maybe we need a reference for this... JB: I am not actually sure about this -- may need to remove.

\red
Figure 2: Were any zeros encountered for the negative binomial or Poisson distributions? Was a shifted log transformation used rather than an unshifted log transformation?

\black 
As indicated in the Figure legend ("Expected CRPS was computed on the natural scale (left), after applying a square-root transformation (middle), and after adding one and applying a log-transformation to the data (right)), we have added 1 before applying the log transformation to deal with zero values.

\blue
L215: “is mainly driven” — Please add pointer to justification (e.g., Figure 7 / discussion).

\black
We added a reference to Figure 7.

@@

\blue
L344: “take differences between forecasts on the log scale” — Clarify.

L345: “divide each forecast by the forecast” — Caveat about current forecast formats should be included here / in following sentences, without (one mention of) the idea about directly soliciting forecasts of week-on-week ratios in between.

\black
We updated the paragraph which now reads:

\textit{We suggested using the natural logarithm as a variance-stabilising transformation (VST). This is appropriate for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$).

### 2023-06-06 main.tex
Addressing some review comments

If case numbers are evolving based on an exponential process and the  modelling task revolves around estimating and forecasting the reproduction number or the corresponding growth rate, then evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number or growth rate) less than overprediction by the same amount. This is because for exponential processes errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate. 
If one is to measure the ability of forecasts to assess and forecast the underlying infection dynamics, it may thus be more desirable to evaluate errors on the growth rate directly.

@@

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation (referred to as the log-transformation in the remainder of this manuscript) in the context of epidemic phenomena. For a prediction target with strictly positive support, the CRPS after applying a log-transformation is given by
%
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F_{\log}, \log y) = \int_{-\infty}^\infty \left( F_{\log}(x) - \boldsymbol{1}(x \geq \log y) \right)^2 dx.
\end{equation}    
\end{linenomath*}
%
Here, $y$ is again the observed outcome and $F_{\log}$ is the predictive CDF of the log-transformed outcome, i.e.,
\begin{linenomath*}
\begin{equation}
F_{\log}(x) = F(\exp(x)),
\end{equation}    
\end{linenomath*}
with $F$ the CDF on the original scale. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic.

@@

Another interpretation for the log-transform is possible if the generative process is framed as exponential with a time-varying growth rate $r(t)$~\citep[see, e.g.,][]{wallingaHowGenerationIntervals2007}, i.e.
\begin{linenomath*}
\begin{equation}
\frac{d}{dt}y(t) = r(t)y(t)
\end{equation}
\end{linenomath*}
%
which is solved by
%
\begin{linenomath*}
\begin{equation}
y(t) = y_0 \exp \left( \int_0^t r(t') dt' \right) = y_0 \exp (\bar{r}t)
\end{equation}
\end{linenomath*}
where $y_0$ is an initial data point and $\bar{r}$ is the mean of the growth rate between the initial time point $0$ and time $t$.

If a forecast $\hat{y}(t)$ for the value of the time series at time $t$ is issued at time 0 based on the data point $y_0$ then the absolute error after log transformation is
%
\begin{linenomath*}
\begin{align}
\begin{split}
\epsilon^* &= \left| \log \left[ \hat{y}( t ) \right] - \log \left[ y ( t ) \right] \right|\\
           &= \left| \log \left[ y_0 \exp (\bar{\hat{r}} t ) \right] - \log \left[ y_0 \exp (\bar{r}t) \right] \right|\\
           &= t \left| \bar{\hat{r}} - \bar{r} \right|
\end{split}
\end{align}
\end{linenomath*}
%
where $\bar{\hat{r}}$ is the true mean growth rate and $\bar{r}$ is the forecast mean growth rate. We thus evaluate the error in the mean exponential growth rate, scaled by the length of the time period considered. Again generalising this to the CRPS and WIS implies a probabilistic evaluation of forecasts of the epidemic growth rate.

@@

Specifically, if the predictive distribution for the quantity $Y$ equals the true data-generating process $F$ (an ideal forecast), the expected CRPS is given by \citep{gneitingStrictlyProperScoring2007}
\begin{linenomath*}
\begin{equation}
\mathbb{E}[\text{CRPS}(F, y)] = 0.5\times\mathbb{E}|Y - Y'|,
\end{equation}
\end{linenomath*}
where $Y$ and $Y'$ are independent samples from $F$. This corresponds to half the \textit{mean absolute difference}, which is a measure of dispersion. If $F$ is well-approximated by a normal distribution $\text{N}(\mu, \sigma^2)$, the approximation
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}(F, y)] \approx \frac{\sigma}{\sqrt{\pi}}
\end{equation}
\end{linenomath*}
can be used. This means that the expected CRPS scales roughly with the standard deviation, which in turn typically increases with the mean in epidemiological forecasting. In order to make the expected CRPS independent of the expected outcome, a \textit{variance-stabilising transformation} \citep[VST,][]{bartlettSquareRootTransformation1936} can be employed. The choice of this transformation depends on the mean-variance relationship of the underlying process.

@@

If the variance is linear with $\sigma^2 = c \times \mu$, as with a Poisson-distributed variable, the square root is known to be a VST. 
Denoting by $F_{\sqrt{\ }}$ the predictive distribution for $\sqrt{Y}$, the delta method can again be used to show that
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\sqrt{\ }}, \sqrt{y}\}] \approx \frac{\sigma/\sqrt{\mu}}{2\sqrt{\pi}} = \frac{\sqrt{c}}{2\sqrt{\pi}}
.
\end{equation}
\end{linenomath*}

@@

Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is mainly driven by the order of magnitude of scores for different forecast targets across time, location and target type and less so by the kind of changes in model rankings for single forecasts discussed above. Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on the relationship between the mean and variance of the forecast target, a log-transformation may even lead to systematically larger scores assigned to small forecast targets, as illustrated in Figure \ref{fig:SIM-wis-state-size-mean}.

@@

\begin{table}
\centering
\begin{tabular}{ccrrrrrr}
\toprule
Horizon & Target & $\alpha$ & $\beta$ & $\alpha_\sqrt{\ }$ & $\beta_\sqrt{\ }$ & $\alpha_\log$ & $\beta_\log$ \\
\midrule
all & all & -1.093 & 0.963 & -0.352 & 0.201 & 0.391 & 0.001\\
\addlinespace
all & Cases & 0.036 & 0.858 & 0.043 & 0.201 & 0.751 & -0.033\\
all & Deaths & -0.884 & 0.868 & 0.273 & 0.121 & 0.436 & -0.023\\
\addlinespace
1 & all & -1.402 & 0.923 & 0.320 & 0.088 & 0.318 & -0.014\\
2 & all & -1.221 & 0.967 & 0.112 & 0.164 & 0.364 & -0.003\\
3 & all & -1.001 & 0.984 & -0.094 & 0.241 & 0.410 & 0.008\\
4 & all & -0.757 & 0.986 & 0.000 & 0.299 & 0.469 & 0.015\\
\addlinespace
1 & Cases & -0.862 & 0.876 & 0.790 & 0.087 & 0.433 & -0.024\\
2 & Cases & -0.243 & 0.877 & 0.959 & 0.162 & 0.660 & -0.031\\
3 & Cases & 0.372 & 0.855 & 1.109 & 0.238 & 0.882 & -0.037\\
4 & Cases & 0.816 & 0.837 & 1.645 & 0.296 & 1.009 & -0.036\\
\addlinespace
1 & Deaths & -1.146 & 0.832 & 0.457 & 0.048 & 0.376 & -0.035\\
2 & Deaths & -0.981 & 0.867 & 0.443 & 0.084 & 0.416 & -0.028\\
3 & Deaths & -0.807 & 0.885 & 0.349 & 0.131 & 0.453 & -0.019\\
4 & Deaths & -0.602 & 0.891 & 0.125 & 0.194 & 0.501 & -0.011\\
\bottomrule
\end{tabular}
\caption{Coefficients of three regressions for the effect of the magnitude of the median forecast on expected scores. The first regression was 
$\log[\text{WIS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], $ where $F$ is the predictive distribution and $y$ the observed value. The second one was 
$\text{WIS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},$ where $F_{\log}$ is the predictive distribution for $\log y$. The third one was $\text{WIS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{sqrt{\ }} + \beta_{sqrt{\ }} \cdot \sqrt{(\text{median}(F))},$ where $F_{\sqrt{\ }}$ is the predictive distribution for $\sqrt{y}$.
}
\label{tab:HUB-regression}
\end{table}

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. 
We suggested using the natural logarithm as a variance-stabilising transformation (VST) for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$, or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. Potentially, the variance stabilising time-series forecasting literature may be a useful source of other transformations for various forecast settings.

@@

Exploring transformations is a promising avenue for future work that could help bridge the gap between modellers and policymakers by providing scoring rules that better reflect what forecast consumers care about. In this paper, we did not make any particular assumptions about what policy makers care about. Rather, we aimed to enable users to make an informed choice by showing how different transformations lead to different relative weights for the kinds of prediction errors forecast consumers may care about, such as absolute vs. relative errors or the size of penalties for over- vs. underprediction. In practice, engagement with decision makers is important to determine what their priorities are and how different ways to measure predictive importance should be weighed.

>>>>

If case numbers are evolving based on an exponential process and the  modelling task revolves around estimating and forecasting the reproduction number or the corresponding growth rate, then evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number or growth rate) less than overprediction by the same amount. Consider a forecast that misses the correct growth rate by either $+\epsilon$ or $-\epsilon$:

\begin{linenomath*}
\begin{equation}
\left| \frac{x_t e^{(r_t + \epsilon) \Delta t} - x_t e^{r_t \Delta t}}{x_t e^{(r_t - \epsilon) \Delta t} - x_t e^{r_t \Delta t}} \right| = e^{\epsilon\Delta t}
\end{equation}
\end{linenomath*}

For exponential processes errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate. 
If one is to measure the ability of forecasts to assess and forecast the underlying infection dynamics, it may thus, conceptually, be more desirable to evaluate errors on the growth rate directly.

@@

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation in the context of epidemic phenomena. We refer to this transformation as 'log-transformation' and to scores that have been log-transformed as scores 'on the log scale' (as opposed to scores 'on the natural scale', which have not been transformed). In the theoretical discussion in Section \ref{sec:methods}, 'log-transformation' and 'log scale' generally refer to a transformation of $\log_{e}(x)$. For practical applications (Section \ref{sec:HUB}) we also use these terms to describe a transformation of $\log_{e}(x + \varepsilon)$ in order to keep the notation simple. For a prediction target with strictly positive support, the CRPS after applying a log-transformation is given by
%
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F_{\log}, \log y) = \int_{-\infty}^\infty \left( F_{\log}(x) - \boldsymbol{1}(x \geq \log y) \right)^2 dx.
\end{equation}    
\end{linenomath*}
%
Here, $y$ is again the observed outcome and $F_{\log}$ is the predictive CDF of the log-transformed outcome, i.e.,
\begin{linenomath*}
\begin{equation}
F_{\log}(x) = F(\exp(x)),
\end{equation}    
\end{linenomath*}
with $F$ the CDF on the original scale. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic.

@@

Another interpretation for the log-transform is possible if the generative process is framed as exponential with a time-varying growth rate $r(t)$~\citep[see, e.g.,][]{wallingaHowGenerationIntervals2007}, i.e.
\begin{linenomath*}
\begin{equation}
\frac{d}{dt}y(t) = r(t)y(t)
\end{equation}
\end{linenomath*}
%
which is solved by
%
\begin{linenomath*}
\begin{equation}
y(t) = y_0 \exp \left( \int_0^t r(t') dt' \right) = y_0 \exp (\bar{r_t}t)
\end{equation}
\end{linenomath*}
where $y_0$ is an initial data point and $\bar{r_t}$ is the mean of the growth rate between the initial time point $0$ and time $t$.

If a forecast $\hat{y}(t)$ for the value of the time series at time $t$ is issued at time 0 based on the data point $y_0$ then the absolute error after log transformation is
%
\begin{linenomath*}
\begin{align}
\begin{split}
\epsilon^* &= \left| \log \left[ \hat{y}( t ) \right] - \log \left[ y ( t ) \right] \right|\\
           &= \left| \log \left[ y_0 \exp (\hat{\bar{r_t}} t ) \right] - \log \left[ y_0 \exp (\bar{r_t}t) \right] \right|\\
           &= t \left| \hat{\bar{r_t}} - \bar{r_t} \right|
\end{split}
\end{align}
\end{linenomath*}
%
where $\bar{r_t}$ is the true mean growth rate and $\hat{\bar{r_t}}$ is the forecast mean growth rate. We thus evaluate the error in the mean exponential growth rate, scaled by the length of the time period considered. Again generalising this to the CRPS and WIS implies a probabilistic evaluation of forecasts of the epidemic growth rate.

@@

Specifically, if the predictive distribution for the quantity $Y$ equals the true data-generating process $F$ (an ideal forecast), the expected CRPS is given by \citep{gneitingStrictlyProperScoring2007}
\begin{linenomath*}
\begin{equation}
\mathbb{E}[\text{CRPS}(F, y)] = 0.5\times\mathbb{E}|Y - Y'|,
\end{equation}
\end{linenomath*}
where $Y$ and $Y'$ are independent samples from $F$. This corresponds to half the \textit{mean absolute difference}, which is a measure of dispersion. If $F$ is well-approximated by a normal distribution $\text{N}(\mu, \sigma^2)$, the approximation
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}(F, y)] \approx \frac{\sigma}{\sqrt{\pi}}
\end{equation}
\end{linenomath*}
can be used. This means that the expected CRPS scales roughly with the standard deviation, which in turn typically increases with the mean in epidemiological forecasting. In order to make the expected CRPS independent of the expected outcome, a \textit{variance-stabilising transformation} \citep[VST,][]{bartlettSquareRootTransformation1936, dunnGeneralizedLinearModels2018} can be employed. The choice of this transformation depends on the mean-variance relationship of the underlying process.

@@

If the variance is linear with $\sigma^2 = c \times \mu$, as with a Poisson-distributed variable, the square root is known to be a VST \citep{dunnGeneralizedLinearModels2018}. 
Denoting by $F_{\sqrt{\ }}$ the predictive distribution for $\sqrt{Y}$, the delta method can again be used to show that
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\sqrt{\ }}, \sqrt{y}\}] \approx \frac{\sigma/\sqrt{\mu}}{2\sqrt{\pi}} = \frac{\sqrt{c}}{2\sqrt{\pi}}
.
\end{equation}
\end{linenomath*}

@@

Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores usually is mainly driven by the order of magnitude of scores for different forecast targets across time, location and target type and less so by the kind of changes in model rankings for single forecasts discussed above (see Figure \ref{fig:HUB-cors} for a practical example). Large observations will dominate average CRPS values when evaluation is done on the natural scale, but much less so after log transformation. Depending on the relationship between the mean and variance of the forecast target, a log-transformation may even lead to systematically larger scores assigned to small forecast targets, as illustrated in Figure \ref{fig:SIM-wis-state-size-mean}.

@@

\begin{table}
\centering
\begin{tabular}{ccrrrrrr}
\toprule
Horizon & Target & $\alpha$ & $\beta$ & $\alpha_\sqrt{\ }$ & $\beta_\sqrt{\ }$ & $\alpha_\log$ & $\beta_\log$ \\
\midrule
% all & all & -1.093 & 0.963 & -0.352 & 0.201 & 0.391 & 0.001\\
% \addlinespace
% all & Cases & 0.036 & 0.858 & 0.043 & 0.201 & 0.751 & -0.033\\
% all & Deaths & -0.884 & 0.868 & 0.273 & 0.121 & 0.436 & -0.023\\
% \addlinespace
% 1 & all & -1.402 & 0.923 & 0.320 & 0.088 & 0.318 & -0.014\\
% 2 & all & -1.221 & 0.967 & 0.112 & 0.164 & 0.364 & -0.003\\
% 3 & all & -1.001 & 0.984 & -0.094 & 0.241 & 0.410 & 0.008\\
% 4 & all & -0.757 & 0.986 & 0.000 & 0.299 & 0.469 & 0.015\\
\addlinespace
1 & Cases & -0.862 & 0.876 & 0.790 & 0.087 & 0.433 & -0.024\\
2 & Cases & -0.243 & 0.877 & 0.959 & 0.162 & 0.660 & -0.031\\
3 & Cases & 0.372 & 0.855 & 1.109 & 0.238 & 0.882 & -0.037\\
4 & Cases & 0.816 & 0.837 & 1.645 & 0.296 & 1.009 & -0.036\\
\addlinespace
1 & Deaths & -1.146 & 0.832 & 0.457 & 0.048 & 0.376 & -0.035\\
2 & Deaths & -0.981 & 0.867 & 0.443 & 0.084 & 0.416 & -0.028\\
3 & Deaths & -0.807 & 0.885 & 0.349 & 0.131 & 0.453 & -0.019\\
4 & Deaths & -0.602 & 0.891 & 0.125 & 0.194 & 0.501 & -0.011\\
\bottomrule
\end{tabular}
\caption{Coefficients of three regressions for the effect of the magnitude of the median forecast on expected scores. The first regression was 
$\log[\text{WIS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], $ where $F$ is the predictive distribution and $y$ the observed value. The second one was 
$\text{WIS}(F_{\log}, \log y) = \alpha_{\log} + \beta_{\log} \cdot \log{(\text{median}(F))},$ where $F_{\log}$ is the predictive distribution for $\log y$. The third one was $\text{WIS}(F_{\sqrt{\ }}, \sqrt{y}) = \alpha_{sqrt{\ }} + \beta_{sqrt{\ }} \cdot \sqrt{(\text{median}(F))},$ where $F_{\sqrt{\ }}$ is the predictive distribution for $\sqrt{y}$.
}
\label{tab:HUB-regression}
\end{table}

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. 
We suggested using the natural logarithm as a variance-stabilising transformation (VST). This is appropriate for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$). Alternatively, the square-root transformation can be appropriate in the case of a Poisson distributed variable \citep{dunnGeneralizedLinearModels2018}. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. Potentially, the variance stabilising time-series forecasting literature may be a useful source of other transformations for various forecast settings.

@@

Exploring transformations is a promising avenue for future work that could help bridge the gap between modellers and policymakers by providing scoring rules that better reflect what forecast consumers care about. {In this paper, we did not make any particular assumptions about policy makers' priorities and preferences. Rather, we aimed to enable users to make an informed choice by showing how different transformations lead to different relative weights for the kinds of prediction errors forecast consumers may care about, such as absolute vs. relative errors or the size of penalties for over- vs. underprediction. In practice, engagement with decision makers is important to determine what their priorities are and how different ways to measure predictive importance should be weighed.
